Constraint Validation with OWL 2 | Closed World Semantics | With and Without Reasoning

### 2014-10-03 paper/paper2.tex
presentations
DC 2014 tutorial

@@

>>>>

\subsection{example validation + inferencing with CWA/UNA}

\begin{ex}
Let's take an example schema:

  my:IssueShape {
    x:submitter @my:SubmitterShape
  }
  my:SubmitterShape {
    foaf:name LITERAL
  }

We can express that as OWL CWA/UNA like so:

  x:submitter a owl:ObjectProperty .

  my:IssueType
    rdfs:subClassOf
      [ owl:onProperty x:submitter ;
        owl:cardinality 1 ] ,
      [ owl:onProperty x:submitter ;
        owl:allValuesFrom my:SubmitterType ] .

  foaf:givenName a owl:DatatypeProperty ;
    rdfs:range xsd:string .
  foaf:familyName a owl:DatatypeProperty ;
    rdfs:range xsd:string .

  my:SubmitterType
    rdfs:subClassOf
      [ owl:onProperty foaf:givenName ;
        owl:cardinality 1 ] ,
      [ owl:onProperty foaf:familyName ;
        owl:cardinality 1 ] .

A piece of instance data like

  <Issue1> x:submitter _:submitter .
  _:submitter foaf:givenName "Bob" .

has two untyped nodes. In order to validate, We posit that:

  <Isseu1> a my:IssueType .

and the system then gets to infer that:

  _:submitter a my:SubmitterType .

(Of course, this could have been an anonymous class in the OWL, but I
gave it a label for clarity here.) CWA validation leads us to believe
that the foaf:familyName property is missing for _:submitter.

If any arcs are missing from _:submitter other than a type arc, those
are considered validation errors, but in order to even validate, I
believe that OWL UNA/CWA (e.g. ICV) is required to do type inferencing
in order to get anything done. It was this juxtaposition that I was
trying to point out.
\end{ex}

@@

\section{constraints vs. axioms}

see R-201-SEPARATION-OF-CONSTRAINTS-AND-ONTOLOGY-SEMANTICS
